Finding shortest and closest vectors in a lattice of Voronoi's first kind

### 2014-04-24 talk/presentation.tex
minor
removed chaff

\newtheorem{proposition}{Proposition}

\frame{
\frametitle{A series of relevant vectors}
 \begin{proposition}
 There is a finite number $K$ such that 
\[
x_K, x_{K+1}, x_{K+2}, \dots
\]
 are all closest points to $y$.
 \end{proposition}
}

\frame{
\frametitle{A series of relevant vectors}
\begin{itemize}
\item The number $K$ of iterations might be large.
\item The initial point $x_0$ affects $K$.
\item Minimising over the set of relevant vectors, that is computing
\[
\arg\min_{ v \in \relevant(\Lambda) \cup \{0\} } \|y - x_k - v \|
\]
might be expensive.
\item There are as many as $2^{n+1}-2$ relevant vectors.
\end{itemize}
}

\frame{
\frametitle{A series of relevant vectors}
For a lattice of Voronoi's first kind:
\begin{itemize}
\item $x_0$ can be chosen to ensure that a closest lattice point in found after at most $K \leq n$ iterations.
\item Minimisation over the set of relevant vectors can be performed by computing a minimum cut in a flow network.
\item Using known algorithms a minimum cut can be found in $O(n^3)$ operations.
\item In total $O(n^4)$ operations are required to compute a closest lattice point.
\end{itemize}
}

@@

\begin{theorem}
Let $\Lambda$ be a $n$-dimensional lattice of Voronoi's first kind with obtuse superbase $b_1, \dots, b_{n+1}$.  Let $z_1,\dots,z_{n+1} \in \reals$ minimise
\[
\| y - \sum_{n=1}^{n+1} b_i z_i \| 
\]
and put
\[
x_0 = \sum_{n=1}^{n+1} b_i \floor{z_i}.
\]
The iterative procedure, initialized at $x_0$, converges to a closest lattice point in at most $K \leq n$ iterations.
\end{theorem}
}

>>>>

% \newtheorem{proposition}{Proposition}

% \frame{
% \frametitle{A series of relevant vectors}
%  \begin{proposition}
%  There is a finite number $K$ such that 
% \[
% x_K, x_{K+1}, x_{K+2}, \dots
% \]
%  are all closest points to $y$.
%  \end{proposition}
% }

\frame{
\frametitle{A series of relevant vectors}
\begin{itemize}
\item The number of iterations depends on $x_0$ and might be large.
\item Minimising over the set of relevant vectors, that is computing
\[
\arg\min_{ v \in \relevant(\Lambda) \cup \{0\} } \|y - x_k - v \|
\]
might be expensive.
\item There are as many as $2^{n+1}-2$ relevant vectors.
\end{itemize}
}

\frame{
\frametitle{A series of relevant vectors}
For a lattice of Voronoi's first kind:
\begin{itemize}
\item $x_0$ can be chosen to ensure that a closest lattice point in found after at most $n$ iterations.
\item Minimisation over the set of relevant vectors can be performed by computing a minimum cut in a flow network.
\item Using known algorithms a minimum cut can be found in $O(n^3)$ operations.
\item In total $O(n^4)$ operations are required to compute a closest lattice point.
\end{itemize}
}

@@

\begin{theorem}
Let $\Lambda$ be a $n$-dimensional lattice of Voronoi's first kind with obtuse superbase $b_1, \dots, b_{n+1}$.  Let $z_1,\dots,z_{n+1} \in \reals$ minimise
\[
\| y - \sum_{i=1}^{n+1} b_i z_i \| 
\]
and put
\[
x_0 = \sum_{i=1}^{n+1} b_i \floor{z_i}.
\]
The iterative procedure, initialized at $x_0$, converges to a closest lattice point in at most $n$ iterations.
\end{theorem}
}
